Estimating Uncertainty for Tipping Points with Deep Learning

### 2022-05-05 manuscript/manuscript.Rmd
Premptive commit

Lastly, we examine how deep learning algorithms perform.
Over the past decade, deep learning has become popular for a broad range of challenging predictive tasks.
However, there have been a relatively small number of studies investigating how deep learning methods perform with sequence to sequence time series forecasting [@kao, @lyu, @Du].
Across these studies, it has become established that using memory or attention-based neural networks, and an encoder-decoder architecture is important to improving forecasting performance. 
To investigate these assertions, we examine four models that use a combination of memory, attention and encoder-decoder network architectures.

>>>>

Over the past decade, deep learning has become popular for a broad range of challenging predictive tasks;
However, there have been a relatively small number of studies investigating how deep learning methods perform with sequence to sequence time series forecasting [@kao, @lyu, @Du].
Across these studies, it has become established that using memory or attention-based neural networks, and an encoder-decoder architecture is important to optimizing forecasting performance. 
To investigate these assertions, we examine four models that use a combination of memory, attention and encoder-decoder network architectures.
